---
title: "Analysis"
format: html
editor: visual
---

## Contributors to Greenhouse Gas Emissions

Agriculture and Land Use Change & Forestry are significant contributors to greenhouse gas emissions. They contribute to about 60% of the overall greenhouse gas emissions across Brazil. There has been an increasing trend of greenhouse gas emissions from these 2 industries from 2015 to 2020 as well. 
<br>
<br>
```{r, include=FALSE, eval=TRUE}
library(tidyverse)
library(plotly)
historical_emissions <- read_csv("historical_emissions.csv")
```

```{r, echo=FALSE, eval=TRUE}
plot_ly(historical_emissions, x = ~year) %>%
  add_trace(y = ~(agriculture * 100 / total), type = 'bar', name = 'Agriculture', marker = list(color = '#B2AC88')) %>%
  add_trace(y = ~(land_use_change_and_forestry * 100 / total), type = 'bar', name = 'Land Use Change & Forestry', marker = list(color = '#D4E5D2')) %>%
  layout(title = "Contributions to Total Emissions",
         xaxis = list(title = "Year"),
         yaxis = list(title = "Percentage of Emissions (%)"),
         barmode = 'stack')
```
<br>
<div style="text-align: center;">
([Climate Watch Data, n.d.](https://www.climatewatchdata.org/countries/BRA?calculation=PER_CAPITA&end_year=2020&start_year=1990){target="_blank"})
</div>
<br>
Hence, there is a need to draw attention to these industries and what exactly contributes to the emission of greenhouse gases.

## Crops & Production

The most commonly produced crops in Brazil are as follows. Interact with the device to learn more about the agriculture and meat production statistics in Brazil from 2011 to 2020.

<iframe height= 1900p width="100%" frameborder="no" src="https://eexvqn.shinyapps.io/myshinyapp/">
</iframe>

Based on the graphs, 